PANCHANGE_analysis

### 2020-08-20 PANCHANGE_analysis.Rmd
added more plots and tables

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(patchwork)
library(broom)
library(tidyverse)
```

@@

# Data availability
```{r gad availability}
dat.raw %>%
  freq(
    data_group_gad,
    cumul = F)
```

```{r phq availability}
dat.raw %>%
  freq(
    data_group_phq,
    cumul = F)
```

```{r pcl availability}
dat.raw %>%
  freq(
    data_group_pcl,
    cumul = F)
```

@@

# ggplot theme
```{r ggplot theme}
theme_personal <-  theme(
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    axis.title.y = element_blank(), 
    legend.background = element_blank(),
    legend.box.background = element_blank(),
    panel.background = element_blank(), 
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_line(
      colour = "gray",
      linetype = "dashed",
      size = 0.2
      ),
    axis.ticks = element_blank()
    )
```

@@

@@

```{r Disorder by Gender}
Disorder_by_Gender <- dat.long.psych %>%
  filter(Diagnosis == 1) %>%
  group_by(Disorder, Gender) %>%
  count(Disorder)

@@

Ethnicity should be recoded
European
Mixed or multiple ethnic origins
African or African British
Asian or Asian British
Arab
```{r Disorder by Ethnicity}
Disorder_by_Ethnicity <- dat.long.psych %>%
  filter(Diagnosis == 1) %>%
  group_by(Disorder, Ethnicity) %>%
  count(Disorder)
```

@@

# Ethnicity
```{r Ethnicity per Sample}
Ethnicity_by_Sample <- dat %>%
  group_by(Ethnicity, Sample) %>%
  count(Ethnicity)

@@

# Gender
```{r Gender per Sample}
dat %>%
  group_by(Gender, Sample) %>%
  count(Gender)
```

>>>>

Install packages
```{r}
#install.packages("infer")
```

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(infer)
library(patchwork)
library(broom)
library(tidyverse)
```

@@

# Data availability

Data availability GAD
```{r gad availability}
dat.raw %>%
  freq(
    data_group_gad,
    cumul = F)
```

Data availability PHQ
```{r phq availability}
dat.raw %>%
  freq(
    data_group_phq,
    cumul = F)
```

Data availability PCL
```{r pcl availability}
dat.raw %>%
  freq(
    data_group_pcl,
    cumul = F)
```

@@

@@

# ggplot theme
Set up ggplot theme for the plots
```{r ggplot theme}
theme_personal <-  theme(
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    axis.title.y = element_blank(), 
    legend.background = element_blank(),
    legend.box.background = element_blank(),
    panel.background = element_blank(), 
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_line(
      colour = "gray",
      linetype = "dashed",
      size = 0.2
      ),
    axis.ticks = element_blank()
    )
```

+++ADD CHUNK FOR AGE CATEGORIES HERE
```{r Age categories}

@@

```{r Disorder by Gender}
Disorder_by_Gender <- dat.long.psych %>%
  filter(Diagnosis == 1) %>%
  count(Disorder, Gender) %>%
  mutate(Prop = round(n/sum(n), 2))

```{r Disorder by Gender}
Disorder_by_Gender <- dat.long.psych %>%
  group_by(Disorder) %>%
  filter(Diagnosis == 1) %>%
  count(Gender) %>%
  mutate(Prop = round(n/sum(n), 2))

@@

Ethnicity should be recoded
European
Mixed or multiple ethnic origins
African or African British
Asian or Asian British
Arab
```{r Disorder by Ethnicity}
Disorder_by_Ethnicity <- dat.long.psych %>%
  filter(Diagnosis == 1) %>%
  count(Disorder, Ethnicity) %>%
  mutate(Prop = round(n/sum(n), 2))

Disorder_by_Ethnicity
```

@@

# Ethnicity
```{r Ethnicity per Sample}
Ethnicity_by_Sample <- dat %>%
  count(Ethnicity, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

@@

# Gender
```{r Gender per Sample prop per total}
dat %>%
  count(Gender, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r Gender per Sample prop per Sample}
dat %>%
  group_by(Sample) %>%
  count(Gender, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r Gender per Sample prop cross table}
dat %>%
  group_by(Sample) %>%
  count(Gender, Sample) %>%
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = Sample, values_from = c(n, Prop))
```

```{r Gender per Sample count cross table}
dat %>%
  count(Gender, Sample) %>%
  spread(key = Sample, value = n)
```

```{r}
dat %>%
  count(Gender, Sample) %>%
  spread(key = Sample, value = n) %>%
  select(-Gender) %>%
  chisq.test() %>%
  glance()
```

```{r Gender per Sample chisquare}
dat %>% 
  specify(Gender ~ Sample)  %>% 
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "Chisq") %>% 
  visualize()# +
#  geom_vline(aes(xintercept = observed_stat), color = "red") # add a vertical line for the data
```
